Conditional selectivity for triplestores

### 2012-09-18 conditional/trunk/selectivity-basic.tex
revert. void:entities -> void:triples
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@378 43ef1190-90fd-4dd7-a769-d0121f02b80e

In the case where there is a given predicate but the subject is a
variable, we can use the \rdfterm{void:distinctSubjects} property:
\begin{equation}\label{eq:selSvPp}
 \sel{S = ? | P = p} =
   \frac{\rdfterm{void:propertyPartition/void:distinctSubjects}}{\rdfterm{void:propertyPartition/void:triples}} ,
\end{equation}
and similarly where the object is a variable:
\begin{equation}\label{eq:selOvPp}
 \sel{O = ? | P = p} =
   \frac{\rdfterm{void:propertyPartition/void:distinctObjects}}{\rdfterm{void:propertyPartition/void:triples}} .
\end{equation}

>>>>

In the case where there is a given predicate but the subject is a
variable, we can use the \rdfterm{void:distinctSubjects} property:
\begin{equation}\label{eq:selSvPp}
 \sel{S = ? | P = p} =
   \frac{\rdfterm{void:propertyPartition/void:distinctSubjects}}{\rdfterm{void:propertyPartition/void:triples}} ,
\end{equation}

In the case where the object is a is a variable, there may be multiple
objects for each predicate in the partition, so we can only say:
\begin{equation}\label{eq:selOvPp}
 \sel{O = ? | P = p} \ge
   \frac{\rdfterm{void:propertyPartition/void:distinctObjects}}{\rdfterm{void:propertyPartition/void:triples}} .
\end{equation}
We note that OWL cardinality constraints may constrain this problem
and that \rdfterm{void:vocabulary} may be used to find the
corresponding ontology.
